shorts: An R Package for Modeling Short Sprints

### 2021-07-24 paper.Rmd
Recompiled

# To predict at "theoretical" distance scale (where force application starts at d=0m)
predict_time_at_distance(
  distance = split_times$distance, 
  MSS = jack_profile_time_estimated$parameters$MSS,
  TAU = jack_profile_time_estimated$parameters$TAU)

>>>>

# To predict at "theoretical" distance scale
#  (where force application starts at d=0m)
predict_time_at_distance(
  distance = split_times$distance, 
  MSS = jack_profile_time_estimated$parameters$MSS,
  TAU = jack_profile_time_estimated$parameters$TAU)

### 2021-07-24 paper.tex
Recompiled

\CommentTok{\# To predict at "theoretical" distance scale (where force application starts at d=0m)}
\FunctionTok{predict\_time\_at\_distance}\NormalTok{(}
  \AttributeTok{distance =}\NormalTok{ split\_times}\SpecialCharTok{$}\NormalTok{distance, }
  \AttributeTok{MSS =}\NormalTok{ jack\_profile\_time\_estimated}\SpecialCharTok{$}\NormalTok{parameters}\SpecialCharTok{$}\NormalTok{MSS,}
  \AttributeTok{TAU =}\NormalTok{ jack\_profile\_time\_estimated}\SpecialCharTok{$}\NormalTok{parameters}\SpecialCharTok{$}\NormalTok{TAU)}
\CommentTok{\#\textgreater{} [1] 1.38 2.12 3.37 4.54 5.67}

@@

\CommentTok{\# Unfortunately, this doesn\textquotesingle{}t work for the distance correction model}
\FunctionTok{predict\_time\_at\_distance}\NormalTok{(}
  \AttributeTok{distance =}\NormalTok{ split\_times}\SpecialCharTok{$}\NormalTok{distance, }
  \AttributeTok{MSS =}\NormalTok{ jack\_profile\_distance\_correction}\SpecialCharTok{$}\NormalTok{parameters}\SpecialCharTok{$}\NormalTok{MSS,}
  \AttributeTok{TAU =}\NormalTok{ jack\_profile\_distance\_correction}\SpecialCharTok{$}\NormalTok{parameters}\SpecialCharTok{$}\NormalTok{TAU,}
  \AttributeTok{distance\_correction =}\NormalTok{ jack\_profile\_distance\_correction}\SpecialCharTok{$}\NormalTok{parameters}\SpecialCharTok{$}\NormalTok{distance\_correction)}
\CommentTok{\#\textgreater{} [1] 1.50 2.23 3.49 4.65 5.78}

>>>>

\CommentTok{\# To predict at "theoretical" distance scale}
\CommentTok{\#  (where force application starts at d=0m)}
\FunctionTok{predict\_time\_at\_distance}\NormalTok{(}
  \AttributeTok{distance =}\NormalTok{ split\_times}\SpecialCharTok{$}\NormalTok{distance, }
  \AttributeTok{MSS =}\NormalTok{ jack\_profile\_time\_estimated}\SpecialCharTok{$}\NormalTok{parameters}\SpecialCharTok{$}\NormalTok{MSS,}
  \AttributeTok{TAU =}\NormalTok{ jack\_profile\_time\_estimated}\SpecialCharTok{$}\NormalTok{parameters}\SpecialCharTok{$}\NormalTok{TAU)}
\CommentTok{\#\textgreater{} [1] 1.38 2.12 3.37 4.54 5.67}

@@

\CommentTok{\# Unfortunately, this doesn\textquotesingle{}t work for the distance correction model}
\FunctionTok{predict\_time\_at\_distance}\NormalTok{(}
  \AttributeTok{distance =}\NormalTok{ split\_times}\SpecialCharTok{$}\NormalTok{distance, }
  \AttributeTok{MSS =}\NormalTok{ jack\_profile\_distance\_correction}\SpecialCharTok{$}\NormalTok{parameters}\SpecialCharTok{$}\NormalTok{MSS,}
  \AttributeTok{TAU =}\NormalTok{ jack\_profile\_distance\_correction}\SpecialCharTok{$}\NormalTok{parameters}\SpecialCharTok{$}\NormalTok{TAU,}
  \AttributeTok{distance\_correction =} 
\NormalTok{    jack\_profile\_distance\_correction}\SpecialCharTok{$}\NormalTok{parameters}\SpecialCharTok{$}\NormalTok{distance\_correction)}
\CommentTok{\#\textgreater{} [1] 1.50 2.23 3.49 4.65 5.78}
